Summary Tables ITHIMR

### 2019-05-03 summary_tables_PA_AP.Rmd
made few changes in summary tables

city<-cities
trans_share<-c(22.5, 40.0, 22.5, 28.1) 
pm_conc<- c(50, 18, 122, 47 )
shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc))
names(shares)[2]<- "trans_share"
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- "emissions"
  summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1)
  print (as.character(cities[x]))
  summary(as.data.frame(summary))
  summary[nrow(summary)+1,1]<-"Transport share"
  summary[nrow(summary),2]<-as.character(shares$trans_share[x])
  summary[nrow(summary)+1,1]<-"PM2.5 Conc"
  summary[nrow(summary),2]<-as.character(shares$pm_conc[x])
  print (summary)

@@

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  x<-ggplot(data_long, aes(x=scenario, y=mmet, fill=scenario)) + geom_boxplot()+ ggtitle(cities[x])+ labs(y="Weekly MMET", x = "Scenarios")
  print(x)

@@

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(mmet),'5th'=quantile(mmet, 0.05),'50th'=quantile(mmet, 0.5),'95th'=quantile(mmet, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[x]))
  print(summary)

@@

for (x in 1: length(cities))
{

@@

print (as.character(cities[x]))
print(summary)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1: length(cities))
{

>>>>

cities<- names(io)
cities<- cities[-2]
trans_share<-c(22.5, 40.0, 22.5, 28.1) 
pm_conc<- c(50, 18, 122, 47 )
city<-cities
shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc))
names(shares)[2]<- "trans_share"
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- "emissions"
  summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1)
  print (as.character(cities[x]))
  summary<-as.data.frame(summary)
  summary[nrow(summary)+1,1]<-"Transport share"
  summary[nrow(summary),2]<-as.character(shares$trans_share[x])
  summary[nrow(summary)+1,1]<-"PM2.5 Conc"
  summary[nrow(summary),2]<-as.character(shares$pm_conc[x])
  print (summary)

@@

cities<- names(io)
cities<- cities[-2]
for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  x<-ggplot(data_long, aes(x=scenario, y=mmet, fill=scenario)) + geom_boxplot()+ ggtitle(cities[x])+ labs(y="Weekly MMET", x = "Scenarios")
  print(x)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
cities<- names(io)
cities<- cities[-2]
for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(mmet),'5th'=quantile(mmet, 0.05),'50th'=quantile(mmet, 0.5),'95th'=quantile(mmet, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[x]))
  print(summary)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
cities<- names(io)
cities<- cities[-2]
for (x in 1: length(cities))
{

@@

print (as.character(cities[x]))
names(summary)<-c("base", "walk", "bike", "car", "MC", "bus")
print(summary)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
cities<- names(io)
cities<- cities[-2]
for (x in 1: length(cities))
{
